---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(crosstalk)
library(d3scatter)
source('global.R')
# bring in 2018 IR ProbMon CDF results
prob <- read_csv('data/allCDF.csv') %>%
  filter(!is.na(Subpopulation), !is.na(Indicator))

# Statewide for practice
#state <- filter(prob, Subpopulation == 'Virginia')
#saveRDS(state, 'data/state.RDS')
#state <- readRDS('data/state.RDS')

#shared data for html widgets
#shared_prob <- SharedData$new(state)#, ~Subpopulation)

shared_prob <- SharedData$new(prob, group='prob_parameter')
shared_prob_VA <- SharedData$new(filter(prob, Subpopulation == "Virginia"), group = 'prob_parameter')


#shared_prob_VA <- SharedData$new(mtcars[mtcars$am == 0,], group = "mtcars_subset")
#sd_mtcars_manual <- SharedData$new(mtcars[mtcars$am == 1,], group = "mtcars_subset")


```

Sidebar {.sidebar}
=====================================
<br><br><br><br><br>
This is a sidebar. And it is global so it is present everywhere.

Choose a ProbMon parameter or parameters to investigate across the different subpopulations.

```{r parameter choice}

filter_select("indicator", "Choose an Indicator", shared_prob, ~Indicator)


```

Statewide
=====================================  

This is where we analyze parameters statewide

Row {data-height=1000}
-------------------------------------
    

### Chart 1
    
```{r statewide}
#filter_select("indicator", "Choose an Indicator", shared_prob, ~Indicator)
d3scatter(shared_prob_VA, ~Value, ~Estimate.P, ~Indicator, width="100%", height=1000)#,
```

Basin
=====================================  

### Chart 1
    
```{r basin}

filter_select("basin", "Choose an Basin", shared_prob, ~Indicator)
#d3scatter(shared_prob, ~Value, ~Estimate.P, ~Indicator, width="100%", height=1000)#,
```


Ecoregion 
=====================================  

Bioregion
=====================================  

Watershed Area
=====================================  

Stream Order
=====================================  

Sample Year
=====================================

Phase
=====================================  

Bay/Non Bay
=====================================  

VSCI Quarters
=====================================  

IR Windows
=====================================  

Stream Size Class
=====================================  



