---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(crosstalk)
library(d3scatter)
library(plotly)
source('global.R')
# bring in 2018 IR ProbMon CDF results
prob <- read_csv('data/allCDF.csv') %>%
  filter(!is.na(Subpopulation), !is.na(Indicator))


percentileSubpop <- function(indicatorDataset, subpopulationDesired, indicatorLookup){
  results <- data.frame(Percentile= NA, MoE = NA)
  for(i in 1:length(subpopulationDesired)){
    rawDat <- filter(indicatorDataset, Subpopulation == subpopulationDesired[i]) %>%
      mutate(MoE.P = StdError.P * 1.96) %>%
      select(Value,Estimate.P, MoE.P) %>% as.data.frame()
    results[i,] <- data.frame(Percentile= as.numeric(vlookup(indicatorLookup,rawDat, 2, TRUE)), 
                              MoE = as.numeric(vlookup(indicatorLookup,rawDat, 3, TRUE)))
  }
  results <- mutate(results, Subpopulation = subpopulationDesired) %>% dplyr::select(Subpopulation, everything())
  return(results)
}

basinSelection <- c("Roanoke Basin", "James Basin", "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York")

# Limit to just VSCI data
VSCI <- filter(prob, Indicator == 'VSCIVCPMI') %>%
  filter(Subpopulation %in% basinSelection)
  
  
#shared data for html widgets
shared_VSCI <- SharedData$new(VSCI)
```


### VSCI by Basin

First build function that takes in an indicator (VSCI), a subpopulation list (basins), and an indicator threshold and split out a dataframe with those percentiles and error bars.
```{r function build, eval=FALSE}

indicatorDataset <- VSCI
subpopulationDesired <- 'Roanoke Basin'#c('Roanoke Basin', 'James Basin')
indicatorLookup <- 60

percentileSubpop <- function(indicatorDataset, subpopulationDesired, indicatorLookup){
  results <- data.frame(Percentile= NA, MoE = NA)
  for(i in 1:length(subpopulationDesired)){
    rawDat <- filter(indicatorDataset, Subpopulation == subpopulationDesired[i]) %>%
      mutate(MoE.P = StdError.P * 1.96) %>%
      select(Value,Estimate.P, MoE.P) %>% as.data.frame()
    results[i,] <- data.frame(Percentile= as.numeric(vlookup(indicatorLookup,rawDat, 2, TRUE)), 
                              MoE = as.numeric(vlookup(indicatorLookup,rawDat, 3, TRUE)))
  }
  results <- mutate(results, Subpopulation = subpopulationDesired) %>% dplyr::select(Subpopulation, everything())
  return(results)
}

percentileSubpop(VSCI, 'James Basin', 60)

percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin'), 60)


basinVSCI <- percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin',  "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York"), 60)
p <- ggplot(basinVSCI,aes(Subpopulation,Percentile))+
  geom_bar(stat='identity', fill="steelblue")+
  labs(title="Percentile by Basins, VSCI = 60", x="Basin", y = "Percentile") +
  #geom_text(aes(label=paste(format(Percentile,digits=3),"%",sep="")), vjust=2, color="white", size=3.5)+
  theme_minimal()+
  theme(legend.position="none",plot.title = element_text(hjust = 0.5))+ # no legend, center title
  theme( # remove the vertical grid lines
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    # explicitly set the horizontal lines (or they will disappear too)
    panel.grid.major.y = element_line( size=.1, color="black" ),
    panel.grid.minor = element_blank(),panel.background = element_blank(),
    axis.line = element_line(colour = "black"))#+ # no background grid

ggplotly(p)
```


```{r just plotly try, eval=FALSE}
plot_ly(basinVSCI, x = ~Subpopulation, y = ~Percentile, type = 'bar' , 
        hoverinfo="text", text=~paste(sep="<br>",
                                      paste("Supopulation: ",Subpopulation),
                                      paste("Percentile:", format(Percentile, digits = 2))))
        
```
    
    

    
    
So maybe make a function that takes in an indicator (VSCI), a subpopulation list (basins), and an indicator threshold and split out a dataframe with those percentiles and error bars, then i can use that dataset for my shared dataset for html selection and plotting.
    
    
```{r statewide, eval=FALSE}
filter_slider("threshold", "Choose an VSCI threshold", shared_VSCI, ~Value)
filter_checkbox('subpopVSCI', 'Choose subpopulations to plot', shared_VSCI, ~Subpopulation, inline = TRUE)
#d3scatter(shared_VSCI, ~Value, ~Estimate.P, ~Indicator)

```


```{r try with shared data}


basinVSCI1 <- percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin',  "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York"), 100) %>% mutate(cutoff=100, narrative= 'Excellent Condition  (VSCI < 100)')
basinVSCI2 <- percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin',  "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York"), 72) %>% mutate(cutoff=72, narrative= 'Good Condition  (VSCI < 72)')
basinVSCI3 <- percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin',  "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York"), 60)%>% mutate(cutoff=60, narrative= 'Moderate Stress (VSCI < 60)')
basinVSCI4 <- percentileSubpop(VSCI, c('Roanoke Basin', 'James Basin',  "Potomac-Shenandoah", "Rappahannock-York", "New", "Chowan",
                    "Tennessee", "Holston", "Big Sandy", "Clinch-Powell", "Potomac", "Shenandoah",
                    "Rappahannock", "York"), 42)%>% mutate(cutoff=42, narrative= 'Severely Stressed (VSCI < 42)')
basinVSCI <- rbind(#basinVSCI1, basinVSCI2,
  basinVSCI3)#, basinVSCI4)






shared_Basin <- highlight_key(basinVSCI3)
shared_Basin2 <- highlight_key(basinVSCI4)
plotly1 <- plot_ly(shared_Basin, x = ~Subpopulation, y = ~Percentile, type = 'bar' , 
                   hoverinfo="text", text=~paste(sep="<br>",
                                      paste("Supopulation: ",Subpopulation),
                                      paste("Percentile:", format(Percentile, digits = 2), 
                                            "+/-", format(MoE, digits = 2))),
        error_y = ~list(array = MoE,
                             color = '#000000'))

bscols(
  #filter_checkbox("cutoff", "Choose a Condition Class", shared_Basin, ~narrative),
  filter_select("subpop", "Select a subpopulation", shared_Basin, ~Subpopulation),
  #plotly1, 
  plot_ly(shared_Basin, x = ~Subpopulation, y = ~Percentile, type = 'bar' , 
                   hoverinfo="text", text=~paste(sep="<br>",
                                      paste("Supopulation: ",Subpopulation),
                                      paste("Percentile:", format(Percentile, digits = 2), 
                                            "+/-", format(MoE, digits = 2))),
        error_y = ~list(array = MoE,
                             color = '#000000')),
  filter_select("subpop2", "Select a subpopulation", shared_Basin2, ~Subpopulation),
plot_ly(shared_Basin2, x = ~Subpopulation, y = ~Percentile, type = 'bar' , 
                   hoverinfo="text", text=~paste(sep="<br>",
                                      paste("Supopulation: ",Subpopulation),
                                      paste("Percentile:", format(Percentile, digits = 2), 
                                            "+/-", format(MoE, digits = 2))),
        error_y = ~list(array = MoE,
                             color = '#000000')),
  widths = c(12, 12)
)

```

